### 2012-06-23 inst/examples/Sethi.Rmd
logistic function was missing max(x-h, 0) step

``` {r }
f <- function(x,h,p){
	S = x - h
	p[1] * S * (1 - S/p[2]) + S
}
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .001
sigma_m <- .001
sigma_i <- .5
````

@@

``` {r biblio, echo=FALSE, results="asis"}
print(knitcitations::bibliography(), style="html")
````

>>>>

``` {r }
f <- function(x,h,p){
  sapply(x, function(x){
  	S = max(x - h, 0)
  	p[1] * S * (1 - S/p[2]) + S
  })
}
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
sigma_m <- .5
sigma_i <- .5
````

@@

``` {r biblio, echo=FALSE, results="asis"}
knitcitations::bibliography("html")
````

### 2012-06-23 inst/examples/voi_sethi_parameters.Rmd
logistic function was missing max(x-h, 0) step

``` {r runall}
lvl <- 0.3
````

``` {r }
det <- scenario(0.01, 0.0, 0.0)
````

``` {r }
g   <- scenario(lvl, 0.0, 0.0)
````

``` {r }
m   <- scenario(0.0, lvl, 0.0)
````

``` {r }
i   <- scenario(0.0, 0.0, lvl)
````

``` {r }
gm  <- scenario(lvl, lvl, 0.0)
````

``` {r }
gi  <- scenario(lvl, 0.0, lvl)
````

``` {r }
mi  <- scenario(0.0, lvl, lvl)
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), smi = c(0, lvl, lvl), sgmi=c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

@@

``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
p1 <- ggplot(dt) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

>>>>

``` {r runall}
lvl <- 0.5
````

``` {r }
det <- scenario(0.00101, 0.001, 0.001)
````

``` {r }
g   <- scenario(lvl, 0.001, 0.001)
````

``` {r }
m   <- scenario(0.001, lvl, 0.001)
````

``` {r }
i   <- scenario(0.001, 0.001, lvl)
````

``` {r }
gm  <- scenario(lvl, lvl, 0.001)
````

``` {r }
gi  <- scenario(lvl, 0.001, lvl)
````

``` {r }
mi  <- scenario(0.001, lvl, lvl)
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list(s0.001=c(0.001,0.001,0.001), sg=c(lvl, 0.001, 0.001), sm=c(0.001, lvl, 0.001), si=c(0.001,0.001,lvl), sgm=c(lvl, lvl, 0.001), sgi=c(lvl, 0.001, lvl), smi = c(0.001, lvl, lvl), sgmi=c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

@@

``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
p1 <- ggplot(subset(dt, fishstock>0)) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````
